### 2018-04-16 paper/paper.tex
adds figures to paper

\documentclass[a4paper]{article}
\usepackage{amsmath, bm}
\usepackage[margin=1in]{geometry}
\begin{document}
\section{Linear Regression}
\subsection{Derivation of Regularized Linear Regression}
asdfasdf

>>>>

\documentclass[a4paper]{article}
\usepackage{amsmath, bm}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\begin{document}
\begin{titlepage}
	\centering
	{\huge \bf Assignment 1\par}
	\vspace{1cm}
	{\Large Computational Intelligence, SS2018\par}
	\vspace{1cm}
	\begin{tabular}{|l|l|l|}
	\hline
	\multicolumn{3}{|c|}{\textbf{Team Members}}   \\ \hline
	Last name & First name & Matriculation Number \\ \hline
	Lee       & Eunseo     & 11739623             \\ \hline
	Shadley   & Alex       & 11739595             \\ \hline
	          &            &                      \\ \hline
	\end{tabular}
\end{titlepage}

\section{Linear Regression}
\subsection{Derivation of Regularized Linear Regression}
asdfasdf

\subsection{Linear Regression with polynomial features}

The following plots demonstrate the results of Linear Regression with polynomial degrees of 1, 2, 5, and 20:

\noindent
\includegraphics[width=0.5\textwidth]{linreg_deg1.png}%
\includegraphics[width=0.5\textwidth]{linreg_deg2.png}\\[2em]
\includegraphics[width=0.5\textwidth]{linreg_deg5.png}%
\includegraphics[width=0.5\textwidth]{linreg_deg20.png}\par
